A novel distributed nature-inspired algorithm for solving optimization problems

### 2021-09-30 paper.tex
ackonledgements section added
Final Updates
Improvements

Where:
\begin{description}  % When enumerating with description, bullet alternatives: cdot, bullet, ast
    \item[$\bullet$ F] is the gravitational force acting between two objects.
    \item[$\bullet$ m1 and m2] are the masses of the objects.
    \item[$\bullet$ r]	is the distance between the centers of their masses.
    \item[$\bullet$ G]	is the gravitational constant: 6.67430(15)×10−11 m3⋅kg−1⋅s−2.
\end{description}

@@

\begin{description}  % When enumerating with description, bullet alternatives: cdot, bullet, ast
    \item[$\bullet $Last Gen.] is the generation that found the solution.
    \item[$\bullet $Eval.] is the total number of evaluations the algorithm executed. 
    \item[$\bullet $Time (sec)] is the total elapsed or wall clock time, in seconds. 
    \item[$\bullet $Eval/sec] is the calculated rate of evaluations per second.
\end{description}

>>>>

Where:
\begin{itemize}
    \item[]	    F is the gravitational force acting between two objects.
    \item[]	    m1 and m2 are the masses of the objects.
    \item[]	    r is the distance between the centers of their masses.
    \item[]	    G is the gravitational constant: 6.67430(15)×10−11 m3⋅kg−1⋅s−2.
\end{itemize}

@@

\begin{itemize}
    \item   Last Gen.   is the generation that found the solution.
    \item   Eval.       is the total number of evaluations the algorithm executed. 
    \item   Time (sec)  is the total elapsed or wall clock time, in seconds. 
    \item   Eval/sec    is the calculated rate of evaluations per second.
\end{itemize}
